Bayesian selection of best subsets via hybrid search

### 2020-02-07 Manuscript/computational statistics/version_1/Bayes_Subset_Stat_and_computing_Jin_Goh.tex
major revision 1

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{Heatmap.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
\documentclass[twocolumn,natbib]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{url}
%\usepackage[linkcolor=blue,citecolor=blue]{hyperref}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
\newcommand{\T}{{ \top}} %
\newcommand{\ua}{{\bf a}} %
\newcommand{\ub}{{\bf b}} %
\newcommand{\uI}{{\bf I}} %
\newcommand{\uH}{{\bf H}} %
\newcommand{\uX}{{\bf X}} %
\newcommand{\ux}{{\bf x}} %
\newcommand{\uy}{{\bf y}} %
\newcommand{\ud}{{\bf d}} %
\newcommand{\uv}{{\bf v}} %
\newcommand{\uV}{{\bf V}} %
\newcommand{\uu}{{\bf u}} %
\newcommand{\um}{{\bf m}} %
\newcommand{\0}{{\boldsymbol 0}} %
\newcommand{\1}{{\boldsymbol 1}} %
\newcommand{\ubeta}{{\boldsymbol \beta}} %
\newcommand{\ueta}{{\boldsymbol \eta}} %
\newcommand{\umu}{{\boldsymbol \mu}} %
\newcommand{\bg}{{\boldsymbol \gamma}} %
\newcommand{\uepsilon}{{\boldsymbol \epsilon}} %
\newcommand{\uSigma}{{\boldsymbol \Sigma}} %
\newcommand{\diag}{{\rm diag}} %
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Computational Statistics}
%
\begin{document}

@@

\institute{Shiqiang Jin \at Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
\email{jinsq@ksu.edu}           %  \\
\and
Gyuhyeong Goh \at Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
\email{ggoh@ksu.edu} 
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{abstract}
Over the past decades, variable selection for high-dimensional data has drawn increasing attention. With a large number of predictors, there rises a big challenge for model fitting and prediction. In this paper, we develop a new Bayesian method of best subset selection using a hybrid search algorithm that combines a deterministic local search and a stochastic global search. To reduce the computational cost of evaluating multiple candidate subsets for each update, we propose a novel strategy that enables us to calculate exact marginal likelihoods of all neighbor models simultaneously in a single computation. In addition, we establish model selection consistency for the proposed method in the high-dimensional setting in which the number of possible predictors can increase faster than the sample size. Simulation study and real data analysis are conducted to investigate the performance of the proposed method.
\keywords{Bayesian variable selection \and  Best subset selection \and High-dimensional regression analysis \and Hybrid search algorithm}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}\label{sec:1}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%

%% else use the following coding to input the bibitems directly in the
%% TeX file.
Variable selection plays a key role in recent regression analysis. In many statistical applications, especially in genetics studies, researchers often face situations where the number of candidate predictors is extremely large but the sample size is relatively small, often referred to as high-dimensional regression problems. The most pressing challenge in high-dimensional regression is to identify relevant predictor variables from a large pool of candidates. In an attempt to perform high-dimensional variable selection, a lot of effort has been put into the development of penalized likelihood methods (e.g., \citealt{tibshirani1996regression, fan2001variable, zou2005regularization, zhang2010nearly}). By adding a penalty function to the likelihood criterion, the penalized likelihood method produces sparse solutions that automatically eliminate the irrelevant predictors from the regression model using the zero-estimates.

In this paper, we are interested in selecting the $k$ most important predictors out of $p$ candidates, called best subset selection \citep{hocking1967selection}. It is well known that best subset selection involves nonconvex optimization problems that are computationally intractable in high-dimensional settings. Although some penalized likelihood approaches such as Lasso, elastic net, and MCP provide a convex surrogate for nonconvex optimization, their applicability to best subset selection is still limited \citep{bertsimas2016best}. Meanwhile, a Bayesian approach to best subset selection, called Bayesian subset regression (BSR), has been proposed by \citet{liang:2013bayesian}. Using an adaptive Markov chain Monte Carlo (MCMC) algorithm, called the stochastic approximation Monte Carlo \citep{liang2007stochastic}, BSR finds the best subset by performing a stochastic search over the entire model space. However, the stochastic search with a large number of candidate predictors often raises computational challenges including extremely heavy computation and slow convergence. To overcome this limitation, we introduce a hybrid best subset search algorithm that combines a deterministic local search and a stochastic global search in a Bayesian framework. The main attractive feature of our proposed method is that evaluating all possible candidate models for the next update, which is the most expensive part of computation, is simultaneously accomplished in a single computation.

@@

\begin{eqnarray}
\label{eq:2} m(\uy|\bg) &=&\int f(\uy|\ubeta_{\bg},\sigma^2)\pi(\ubeta_{\bg}|\sigma^2, \bg) \pi(\sigma^2) d\ubeta_\bg d\sigma^2 \nonumber \\

@@

	\uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}  } },

@@

where $f(\uy|\ubeta_{\bg},\sigma^2)$ denotes the reduced model likelihood function given $\bg$ and $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$.

From Bayes' theorem, the posterior model probability of $\bg$ is proportional to $\pi(\bg|\uy)\propto m(\uy|\bg) \pi(\bg)\propto m(\uy|\bg) \mathbb{I}(|\bg|=k )$. Therefore, Bayesian best subset selection can be performed by maximizing $m(\uy|\bg)$ over $\bg$ subject to the constraint $|\bg|=k$. Keep in mind that high-dimensional and non-convex optimization problems arise in our framework.

@@

We introduce a deterministic search algorithm in Algorithm \ref{alg:1} that converges to a local maximum of $m(\uy|\bg)$ subject to $|\bg|=k$.
\begin{algorithm}[H]
\caption{Deterministic best subset search with a fixed $k$}\label{alg:1}
\begin{itemize}\itemsep=0pt
\item[1.] Define $\hat{\bg}$ to be an initial subset of size $k$; and set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[2.] \textbf{Repeat} for $t=1,2,\ldots,$
\begin{itemize}\itemsep=0pt
\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$;\\ \texttt{\# i.e., select the locally best subset of size k+1} 
\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;\\ \texttt{\# i.e., select the locally best subset of size k} 
\item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$; 
\end{itemize}
\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$. \texttt{\# i.e., terminate immediately if no update is made}
\item[3.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
The following theorem proves the convergence of the proposed deterministic search algorithm.
\begin{theorem}\label{thm:1} The deterministic search in Algorithm \ref{alg:1} monotonically increases the objective function, $m(\uy|\bg)$, subject to $|\bg|=k$. In addition, the algorithm terminates in a finite number of iterations.
\end{theorem}
\begin{proof}[of Theorem \ref{thm:1}] Let $\hat{\bg}^{(t-1)}$ be the best subset of size $k$ updated by the ${t-1}$-th iteration. Then, $\hat{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$, where $$\tilde{\bg}^{(t)}=\arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)}  ) } m(\uy|\bg).$$ Since $\hat{\bg}^{(t-1)}$ also belongs to $ \mathcal{N}_-(\tilde{\bg}^{(t)} ) $, we thus have $m(\uy|\hat{\bg}^{(t-1)} ) \leq m(\uy|\hat{\bg}^{(t)}),$ which proves our first statement. Since the number of all possible states of $\bg$ satisfying $|\bg|=k$ is finite, the algorithm terminates in a finite number of iterations. This completes our proof.
\end{proof}
Although the deterministic search algorithm converges rapidly, a possible drawback is that the algorithm can get trapped in a local optimum. As an alternative, we introduce a stochastic search algorithm in Algorithm \ref{alg:2} that converges to a global maximum of $m(\uy|\bg)$ with the constraint $|\bg|=k$.
\begin{algorithm}[ht!]
\caption{Stochastic best subset search with a fixed $k$}\label{alg:2}
\begin{itemize}\itemsep=0pt
\item[1.] Define $\hat{\bg}$ to be an initial subset of size $k$; and set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[2.] \textbf{Repeat} for $t=1,\ldots,T$:
\begin{itemize}\itemsep=0pt
\item[a)] Update $\tilde{\bg}^{(t)}$ by selecting one from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probability $$\frac{m(\uy|\bg)}{\sum_{\bg' \in \mathcal{N}_+(\hat{\bg}^{(t-1)})} m(\uy|\bg')},~\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} );$$ 
\item[b)] Update $\hat{\bg}^{(t)}$ by selecting one from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probability $$\frac{m(\uy|\bg)}{\sum_{\bg' \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg')},~\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) ;$$
\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$.
\end{itemize}
\item[3.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
Note that the proposed stochastic search algorithm generates a Markov chain, $\{\hat{\bg}^{(t)},t=1,\ldots,T\}$, with the state space $\{\bg:|\bg|=k\}$. Hence, if the current estimate $\hat{\bg}$ is not the global maximum, then we must observe that $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$ with probability one as $T\to \infty$. Therefore, as we iterate the algorithm, $\hat{\bg}$ converges to the global maximum.

Although the stochastic search algorithm eventually reaches the global optimum, it requires the large number of iterations, which is computationally inefficient. To develop a computationally efficient global optimization algorithm, we propose a hybrid best subset selection algorithm that combines the stochastic global search algorithm and the deterministic local search algorithm into one. The proposed hybrid search algorithm is given in Algorithm \ref{alg:3}.
\begin{algorithm}[ht!]
\caption{Hybrid best subset search with a fixed $k$}\label{alg:3}
\begin{itemize}\itemsep=0pt
\item[1.] Define an initial model of size $k$ as $\hat{\bg}$.
\item[2.] Set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[\texttt{\#}] \texttt{deterministic search step}
\item[3.] \textbf{Repeat} for $t=1,2,\ldots:$ 
\begin{itemize}\itemsep=0pt
\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$; 
\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;
\item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$;
\end{itemize}
\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$.
\item[4.] Set $\hat{\bg}^{(0)}=\hat{\bg}$ and choose a tuning parameter $\alpha \in (0,1]$.
\item[\quad \texttt{\#}] \texttt{stochastic search step}
\item[5.] \textbf{Repeat} for $t=1,\ldots,T$: 
\begin{itemize}
\item[a)] Update $\tilde{\bg}^{(t)}$ by drawing one from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probability $$\frac{m(\uy|\bg)^\alpha}{\sum_{\bg\in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)^\alpha},~\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} );$$
\item[b)] Update $\hat{\bg}^{(t)}$ by drawing one from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probability $$\frac{m(\uy|\bg)^\alpha}{\sum_{\bg' \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg')^\alpha },~\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} );$$
\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$ and immediately go to Step 2.
\end{itemize}
\item[6.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
In the proposed hybrid search algorithm, the deterministic search is first used to find a local optimum in an efficient manner. Then, the stochastic search is employed to check whether or not the deterministic search algorithm has reached the global optimum. Note that if the stochastic search finds a better subset $\hat{\bg}^{(t)}$ than the current best subset $\hat{\bg}$ (i.e., when $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$ occurs), then we immediately stop the stochastic search procedure and go back to the deterministic search step with the updated state of $\hat{\bg}$. To improve the performance of stochastic search, we introduce a tuning parameter $\alpha \in (0,1]$ which acts as a precision parameter. As $\alpha\to 0$, the distribution will be more spread out so that the chance of getting stuck in the local maximum will be reduced in the stochastic search step. If we set $\alpha=1$, the stochastic search step is analogous to Algorithm \ref{alg:2}. In our simulation study and real data analysis, we set $\alpha=\min\{1,\log(2)/\log( m_{(1)} /  m_{(2)} )\}$, where $m_{(1)}$ and $m_{(2)}$ are, respectively, the first and second largest values of $\{m(\uy|\bg):\bg  \in \mathcal{N}_+(\hat{\bg})\}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required

%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[colorlinks]{hyperref}
%\usepackage{natbib}
\newcommand{\T}{\top} %
\newcommand{\ua}{\bf a} %
\newcommand{\ub}{\bf b} %
\newcommand{\uI}{\bf I} %
\newcommand{\uH}{\bf H} %
\newcommand{\uX}{\bf X} %
\newcommand{\ux}{\bf x} %
\newcommand{\uy}{\bf y} %
\newcommand{\ud}{\bf d} %
\newcommand{\uv}{\bf v} %
\newcommand{\uu}{\bf u} %
\newcommand{\um}{\bf m} %
\newcommand{\0}{\boldsymbol 0} %
\newcommand{\1}{\boldsymbol 1} %
\newcommand{\ubeta}{\boldsymbol \beta} %
\newcommand{\ueta}{\boldsymbol \eta} %
\newcommand{\umu}{\boldsymbol \mu} %
\newcommand{\bg}{\boldsymbol \gamma} %
\newcommand{\uepsilon}{\boldsymbol \epsilon} %
\newcommand{\uSigma}{\boldsymbol \Sigma} %
\newcommand{\diag}{\rm diag}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\institute{S. Jin \at
              Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A. \\
              \email{jinsq@ksu.edu}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           G. Goh \at
              Department of Statistics, Kansas State University, Manhattan, KS 66506, U.S.A.\\
              \email{ggoh@ksu.edu} 
}

% \date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

@@

\begin{abstract}
Over the decades, variable selection with high-dimensional data has drawn increasing attention. With a large number of predictors, there rises a big challenge for model fitting and prediction. In this paper, we develop a new Bayesian method of best subset selection using a hybrid search algorithm that combines a deterministic local search and a stochastic global search. To reduce the computational cost of evaluating multiple candidate subsets for each update, we propose a novel strategy that enables us to calculate exact marginal likelihoods of all neighbor models simultaneously in a single computation. In addition, we establish model selection consistency for the proposed method in the high-dimensional setting in which the number of possible predictors can increase faster than the sample size. Simulation study and real data analysis are conducted to investigate the performance of the newly-developed method.
\keywords{Bayesian variable selection\and Best subset selection\and High-dimensional regression analysis\and Hybrid search algorithm}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}\label{sec:1}
Variable selection plays a key role in recent regression analysis. In many statistical applications, especially in genetics studies, researchers often face situations in which the number of candidate predictors is extremely large but the sample size is relatively small, often referred to as high-dimensional regression problems. The most pressing challenge in high-dimensional regression is to identify relevant predictor variables from a large pool of candidates. In an attempt to perform high-dimensional variable selection, a lot of effort has been put into the development of penalized likelihood methods (e.g., \cite{tibshirani1996regression}, \cite{fan2001variable}, \cite{zou2005regularization}, \cite{zhang2010nearly}). By adding a penalty function to the likelihood criterion, the penalized likelihood method produces sparse solutions that automatically eliminate the irrelevant predictors from the regression model using the zero-estimates.

% For tables use

In this paper, we are interested in selecting the $k$ most important predictors out of $p$ candidates, called best subset selection \cite{hocking1967selection}. It is well known that best subset selection involves non-convex optimization problems that are computationally intractable in high-dimensional settings. Although some penalized likelihood approaches such as Lasso, elastic net, and MCP provide a convex surrogate for non-convex optimization, their applicability to best subset selection is still limited \cite{bertsimas2016best}. Meanwhile, a Bayesian approach to best subset selection, called Bayesian subset regression (BSR), has been proposed by \cite{liang:2013bayesian}. Using an adaptive Markov chain Monte Carlo (MCMC) algorithm, called the stochastic approximation Monte Carlo \cite{liang2007stochastic}, BSR finds the best subset by performing a stochastic search over the entire model space. However, the global stochastic search with a large number of candidate predictors often raises computational challenges including heavy computation and slow convergence. To overcome this limitation, we introduce a hybrid best subset search algorithm that combines a deterministic local search and a stochastic global search in a Bayesian framework. The main attractive feature of our proposed method is that evaluating all possible candidate models for the next update, which is the most expensive part of Bayesian computation, is simultaneously accomplished in a single computation.

@@

\begin{eqnarray}\label{eq:2} 
m(\uy|\bg) &=&\int f(\uy|\ubeta_{\bg},\sigma^2)\pi(\ubeta_{\bg}|\sigma^2, \bg) \pi(\sigma^2) d{\ubeta_{\bg}} d{\sigma^2} \nonumber \\

@@

  \uy+b_{\sigma}\right)^{\frac{a_{\sigma}+n}{2}}},

@@

where $f(\uy|\ubeta_{\bg},\sigma^2)$ denotes the reduced model likelihood function given $\bg$ and $\uH_{\bg} = \uI_n-\uX_{\bg}(\uX_{\bg}^{\T}\uX_{\bg}+\tau^{-1}\uI_{|\bg|})^{-1}\uX_{\bg}^{\T}$. From Bayes' theorem, the posterior model probability of $\bg$ is proportional to $\pi(\bg|\uy)\propto m(\uy|\bg) \pi(\bg)\propto m(\uy|\bg) \mathbb{I}(|\bg|=k )$. Therefore, Bayesian best subset selection can be performed by maximizing $m(\uy|\bg)$ over $\bg$ subject to the constraint $|\bg|=k$. Keep in mind that high-dimensional and non-convex optimization problems arise in our framework.

@@

We introduce a deterministic search algorithm in Algorithm \ref{alg:1} that converges to a local maximum of $m(\uy|\bg)$ subject to $|\bg|=k$.
\begin{algorithm}[H]
\caption{Deterministic best subset search with a fixed $k$}\label{alg:1}
\begin{itemize}\itemsep=0pt
\item[1.] Define $\hat{\bg}$ to be an initial subset of size $k$; and set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[2.] \textbf{Repeat} for $t=1,2,\ldots,$
\begin{itemize}\itemsep=0pt
\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$; \quad \texttt{\# select the best subset of size $k+1$ in $ \mathcal{N}_+(\hat{\bg}^{(t-1)})$ } 
\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;\quad \texttt{\# select the best subset of size $k$ in $ \mathcal{N}_-(\tilde{\bg}^{(t)})$ } 
\item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$; 
\end{itemize}
\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$. \quad \texttt{\# terminate immediately if no update is made}
\item[3.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}

The following theorem proves the convergence of the proposed deterministic search algorithm.
\begin{theorem}\label{thm:1} The deterministic search in Algorithm \ref{alg:1} monotonically increases the objective function, $m(\uy|\bg)$, subject to $|\bg|=k$. In addition, the algorithm terminates in a finite number of iterations.
\end{theorem}
\begin{proof}[of Theorem \ref{thm:1}] Let $\hat{\bg}^{(t-1)}$ be the best subset of size $k$ updated by the ${t-1}$-th iteration. Then, $\hat{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$, where $\tilde{\bg}^{(t)}=\arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)}  ) } m(\uy|\bg)$. Since $\hat{\bg}^{(t-1)}$ also belongs to $ \mathcal{N}_-(\tilde{\bg}^{(t)} ) $, we thus have $m(\uy|\hat{\bg}^{(t-1)} ) \leq m(\uy|\hat{\bg}^{(t)}),$ which proves our first statement. Since the number of all possible states of $\bg$ satisfying $|\bg|=k$ is finite, the algorithm terminates in a finite number of iterations. This completes our proof.
\end{proof}
Although the deterministic search algorithm converges rapidly, a possible drawback is that the algorithm can get trapped in a local optimum. As an alternative, we introduce a stochastic search algorithm in Algorithm \ref{alg:2} that converges to a global maximum of $m(\uy|\bg)$ with the constraint $|\bg|=k$.
\begin{algorithm}[ht!]
\caption{Stochastic best subset search with a fixed $k$}\label{alg:2}
\begin{itemize}\itemsep=0pt
\item[1.] Define $\hat{\bg}$ to be an initial subset of size $k$; and set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[2.] \textbf{Repeat} for $t=1,\ldots,T$:
\begin{itemize}\itemsep=0pt
\item[a)] Sample $\tilde{\bg}^{(t)}$ from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probabilities proportional to ${m(\uy|\bg)}\mathbb{I}\{\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) \}$; 
\item[b)] Sample $\hat{\bg}^{(t)}$ from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probabilities proportional to ${m(\uy|\bg)}\mathbb{I}\{\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) \}$;
\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$.
\end{itemize}
\item[3.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}

Note that the proposed stochastic search algorithm generates a Markov chain, $\{\hat{\bg}^{(t)},t=1,\ldots,T\}$, with the state space $\{\bg:|\bg|=k\}$. Hence, if the current estimate $\hat{\bg}$ is not the global maximum, then we must observe that $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$ with probability one as $T\to \infty$. Therefore, as we iterate the algorithm, $\hat{\bg}$ converges to the global maximum.

However, while the stochastic search algorithm eventually reaches the global optimum, it requires the large number of iterations, which is computationally inefficient. To develop a computationally efficient global optimization algorithm, we propose a hybrid best subset selection algorithm that combines the stochastic global search algorithm and the deterministic local search algorithm into one. The proposed hybrid search algorithm is given in Algorithm \ref{alg:3}.
\begin{algorithm}[ht!]
\caption{Hybrid best subset search with a fixed $k$}\label{alg:3}
\begin{itemize}\itemsep=0pt
\item[1.] Define an initial model of size $k$ as $\hat{\bg}$.
\item[2.] Set $\hat{\bg}^{(0)}=\hat{\bg}$.
\item[3.] \textbf{Repeat} for $t=1,2,\ldots:$ \quad \texttt{\#deterministic search step}
\begin{itemize}\itemsep=0pt
\item[a)] Compute $\tilde{\bg}^{(t)} = \arg\max_{\bg  \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) } m(\uy|\bg)$; 
\item[b)] Compute $\hat{\bg}^{(t)}=  \arg\max_{\bg  \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) } m(\uy|\bg)$;
\item[c)] Update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$;
\end{itemize}
\item[] \textbf{until} $\hat{\bg}^{(t-1)}=\hat{\bg}^{(t)}$.
\item[4.] Set $\hat{\bg}^{(0)}=\hat{\bg}$ and choose a tuning parameter $\alpha \in (0,1]$.
\item[5.] \textbf{Repeat} for $t=1,\ldots,T$: \quad \texttt{\#stochastic search step}
\begin{itemize}
\item[a)] Sample $\tilde{\bg}^{(t)}$ from $\mathcal{N}_+(\hat{\bg}^{(t-1)} )$ with probabilities proportional to ${m(\uy|\bg)^\alpha}\mathbb{I}\{\bg \in \mathcal{N}_+(\hat{\bg}^{(t-1)} ) \}$;
\item[b)] Sample $\hat{\bg}^{(t)}$ from $\mathcal{N}_-(\tilde{\bg}^{(t)} )$ with probabilities proportional to ${m(\uy|\bg)^\alpha}\mathbb{I}\{\bg \in \mathcal{N}_-(\tilde{\bg}^{(t)} ) \}$;
\item[c)] \textbf{If} $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$, \textbf{then} update $\hat{\bg}\leftarrow \hat{\bg}^{(t)}$, break the loop, and go to Step 2.
\end{itemize}
\item[6.] Return $\hat{\bg}$.
\end{itemize}
\end{algorithm}
In the proposed hybrid search algorithm, the deterministic search is first used to find a local optimum in an efficient manner. Then, the stochastic search is employed to check whether or not the deterministic search algorithm has reached the global optimum. Note that if the stochastic search finds a better subset $\hat{\bg}^{(t)}$ than the current best subset $\hat{\bg}$ (i.e., when $m(\uy|\hat{\bg})<m(\uy|\hat{\bg}^{(t)})$ occurs), then we immediately stop the stochastic search procedure and go back to the deterministic search step with the updated state of $\hat{\bg}$. To improve the performance of stochastic search, we introduce a tuning parameter $\alpha \in (0,1]$ which acts as a precision parameter. As $\alpha\to 0$, the distribution will be more spread out so that the chance of getting stuck in the local maximum will be reduced in the stochastic search step. If we set $\alpha=1$, the stochastic search step is analogous to Algorithm \ref{alg:2}. In our simulation study and real data analysis, we set $\alpha=\min\{1,\log(2)/\log( m_{(1)} /  m_{(2)} )\}$, where $m_{(1)}$ and $m_{(2)}$ denote the first and second largest values of $\{m(\uy|\bg)
: \bg  \in \mathcal{N}_+(\hat{\bg}) \}$.
